Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-18 ms.tex
introduction clean-up, added Akari reference

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ resolution maps of dust temperature and optical 
depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, we expect our best-fit parameters to be useful in constructing 
high-resolution
 predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also data near the peak of the dust SED, for
 example \AKARI~140-160$\mu$m. We also anticipate our derived optical depth map
 will serve as a useful comparison for extinction estimates based 
directly upon optical/NIR observations of stars.

>>>>

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust spectral energy distribution (SED) composed
 of \PLANCK~and \IRAS~data. In doing so, we obtain $6.1'$ resolution maps of 
dust temperature and optical depth. Because we employ a model that has been 
validated with FIRAS data down to sub-mm wavelengths, we expect our best-fit 
parameters to be useful in constructing high-resolution predictions of dust 
emission over a very broad range of wavelengths. This includes low frequencies 
($<$350 GHz), which \cite{planckdust} caution their model may not adequately 
fit, and also measurements near the peak of the dust SED, for example 
\AKARI~140-160$\mu$m \citep{akari}. We also anticipate our derived optical 
depth map will serve as a useful comparison for extinction estimates based 
directly upon optical/NIR observations of stars.
